\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-10 paper.tex
Finished theory. No need to present the transfer matrix theory.

\subsection{Transfer Matrix Method (TMM)}
One of the methods used for the analysis of photonic crystal
structures is the transfer matrix method. We use it to investigate the
reflectance of light in a one-dimensional photonic crystal. The
electric and magnetic fields within the layers are shown as $E_m$ and
$H_m$. Then we can specify the electric and magnetic fields in the
air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
\begin{equation}
\left[
\begin{matrix}
E_{_{0}}\\
H_{_{0}}
\end{matrix}
\right]= \textbf{M}_{_{1}}, \textbf{M}_{_{2}},...,\textbf{M}_{_{N}} \left[
\begin{matrix}
E_{_{m}}\\
H_{_{m}}
\end{matrix}
\right]
\end{equation}
Where N is the total number of layers including the cavity layer and $
M_j $ is the matrix characteristic of the layer $ j $ specified by:
\begin{equation}
\textbf{M}_j = \left[
\begin{matrix}
\cos \delta_j & -\frac{i}{\eta_j} \sin \delta_j \\
-i\eta_j \sin\delta_j & \cos\delta_j
\end{matrix}
\right]
\end{equation}
and
\begin{equation}
\delta_j= \frac{2\pi}{\lambda} \tilde{n}_j d_j \cos \theta_j
\end{equation}
where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
is the thickness of the layer, and $ \theta_j $ is the angle of
refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
for layer j is defined as:
\begin{equation}\label{Eq:Mt1}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}}\tilde{n}_j cos\theta_j \hspace{1cm} (TE \ \ mode)
\end{equation}
y
\begin{equation}\label{Eq:Mt2}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}} \frac{\tilde{n}_j}{cos\theta_j} \hspace{1cm} (TM \ \ mode)
\end{equation}
where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
permeability, respectively. The transfer matrix of all the photonic
crystal is given by:
\begin{equation}
\textbf{M}=\textbf{M}_1,\textbf{M}_2,...,\textbf{M}_N= \left[
\begin{matrix}
m_{11} & m_{12} \\
m_{21} & m_{22}
\end{matrix}
\right]
\end{equation}
We can write the reflection and transmission coefficients in a
one-dimensional photonic crystal nanocavity as:
\begin{equation}
r=\frac{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}
\end{equation}
end
\begin{equation}
t=\frac{2\eta_0}{\eta_0(m_{11}m_{12}\eta_m)+(m_{21}m_{22}\eta_m)}
\end{equation}
where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
layers, respectively (as defined in equations \ref{Eq:Mt1} or
\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
the entire photonic crystal nanocavity is given by:
\begin{equation}
R=|r|^{2}
\end{equation}
y
\begin{equation}
T=\frac{\eta_m}{\eta_0}|t|^{2}
\end{equation}
\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
      respectively. (b) It is the diagram of the electrochemical
      cell with its parts: silicon wafer, Teflon cell, platinum
      point electrode, Electrochemical Aqueous solution and the
      connection of the circuit with the cathode and anode. (c)
      It is a schematic drawing of the Cross section of the
      electrochemically attacked porous silicon seen in three
      different regions as mentioned above. }}
    \label{fig:DE1}
  \end{figure}

>>>>

Using Eq. \eqref{Eq:J} we can correlate the local current density at
the sample as it is prepared with its geometric and optical
properties. For the calculation of the optical properties we use the
well known transfer matrix method \notaL{refs}.

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
      respectively. (b) It is the diagram of the electrochemical
      cell with its parts: silicon wafer, Teflon cell, platinum
      point electrode, Electrochemical Aqueous solution and the
      connection of the circuit with the cathode and anode. (c)
      It is a schematic drawing of the Cross section of the
      electrochemically attacked porous silicon seen in three
      different regions as mentioned above. }}
    \label{fig:DE1}
  \end{figure}
